---
title: "Varroa virus knockdown"
output:
  html_document:
    code_folding: hide
    theme: cerulean
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: yes
      df_print: paged
editor_options: 
  chunk_output_type: console
---
<style type="text/css">
  body{
  font-size: 12pt;
}
</style>

In this study we investigated virus-virus and vector-virus interactions by combining two approaches: 

(1) meta-transciptomic analysis, and 
(2) gene-silencing experiments. 

In the following code we analyze the experimental validation of the (2) gene silencing experiments.

The output figures include the original figure 3, in the relevant manuscript [Eliash et al.__](doi)  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries
```{r libraries ,  message=FALSE, warning=FALSE, echo=FALSE}
suppressPackageStartupMessages(library(tidyverse))
library(dplyr)
library(tidyverse)
library(ggplot2)
library(Rmisc)
library(ggpubr)
#library(anchors) not avilable for the current R 
library(broom)
library(HDInterval)
library(coda)
library(brms)
library(devtools)
#library(rjags)
#library(BEST)
library(ggpubr)
library(ggthemes)
library(car) 
library(stats) 
library(moments)
library(intervcomp)
library(grid)
library(formattable)
library(gridExtra)
library(ggsignif)
library(patchwork)
library(cowplot)
library(AMR)
```

## Load data
```{r message=FALSE, warning=FALSE, echo=FALSE}
dat_survival <- read_csv("/Users/nuriteliash/Documents/GitHub/varroa-virus-knockdown/data/RNAi_survival.csv")
dat_virus <- read_csv("/Users/nuriteliash/Documents/GitHub/varroa-virus-knockdown/data/virus_in_silenced.csv")
dat_gene <- read_csv("/Users/nuriteliash/Documents/GitHub/varroa-virus-knockdown/data/Silencing_qPCR.csv")
dat_gene <- dat_gene %>%
  filter((Treatment %in% c("Silenced", "Control"))) %>%
  filter(Time == "48h")
```

## Effect of dsRNA on varroa survival (Fisher exact test)
```{r varroa survival stats, message=FALSE, warning=FALSE}
# for each date, compare the live and dead mite distribution of GFP to each of the dsRNA treatments. 
results_fisher <- data.frame()

for (date in unique(dat_survival$Date))
{
  surv <- dat_survival %>% dplyr::filter(Date == date)
  control <-  surv %>%
     filter(target == "GFP") %>%
     dplyr::select(c(Live,Dead)) %>%
     as.numeric()
  surv_test <- surv %>% filter(! target == "GFP")
 
   for (gene in unique(surv_test$target))
   {
        treatment <- surv_test %>%
           filter(target == gene) %>%
           dplyr::select(c(Live,Dead)) %>%
           as.numeric()
        test <- fisher.test(cbind(control,treatment))   
        results_fisher <- rbind(results_fisher, data.frame(date = date, gene = gene, pvalue = test$p.value))
   }
    
}

# make a clean table for the supplementary information, that include only the silenced genes:
genes <- c("Gly","clmd", "CuP8", "CuP14", "GFP", "Twitch")
results_fisher$exp <- paste(results_fisher$date, results_fisher$gene)
dat_survival$exp <- paste(dat_survival$Date, dat_survival$target)

Table_S6 <- full_join(results_fisher, dat_survival, by = "exp") %>%
    dplyr::filter(grepl(paste(genes, collapse="|"), exp)) %>%
    dplyr::select(Date, target, Live, Dead, pvalue) %>%
    rename(target = "Silenced-gene")

#write_csv(Table_S6, file = "/Users/nuriteliash/Documents/GitHub/varroa-virus-knockdown/results/Table_S6.csv")
```

## Gene expression in dsRNA-treated and control mites
### test for differene in gene expression, between treatment and control (Wilcoxon ranked test)
```{r Gene expression stats, message=FALSE, warning=FALSE}
results_gene <- data.frame()
for (gene in unique(dat_gene$Gene)) 
  {
  test <- wilcox.test(RQ ~ Treatment, alternative = "two.sided", data = filter(dat_gene, Gene == gene))
    results_gene <- rbind(results_gene, data.frame(gene = gene, pvalue = test$p.value))
  }

#We are testing the same knockdown gene several times, creating a multiple comparison problem, we fix that with a FDR correction per gene
### for some reason - the adjusted p-values are the same as the original p-vlaues!
geneExp <- group_by(results_gene, gene) %>% 
  mutate(padj = p.adjust(pvalue, method = "fdr"))
geneExp <- dplyr::rename(geneExp, Gene = gene) #i changed the colname of "gene" to "Gene". for some reason this was disturbing in "filter" function later on. 

#write_csv(geneExp, "/Users/nuriteliash/Documents/GitHub/varroa-virus-knockdown/results/Table_S5.csv")

# plot all genes expression for silenced and control-mites, in a boxplot
boxplot <- list()
for (gene in unique(dat_gene$Gene)) 
{
  table <- filter(dat_gene, Gene == gene)
  N <- nrow(table)
geneExppadj <- filter(geneExp, Gene == gene)
  Padjust <- formattable(as.double(geneExppadj[1,3], digits = 2, format = "f"))
  # Plot
   p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = paste(gene,",Padjust=",Padjust,", n=",N),
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative expression", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=8)) 
  boxplot[[gene]] <- p
}

# plot all 11 genes in one figure
grid.arrange(boxplot$Anl, boxplot$clmd, boxplot$Chl, boxplot$CuP14, boxplot$CuP8, boxplot$Glut, boxplot$Gly, boxplot$HDD, boxplot$Prolin, boxplot$Sar, boxplot$Trans, boxplot$Twitch, nrow = 3, ncol = 4)
#lapply(boxplot, grid.arrange, nrow = 4, ncol = 3)
```

#### Gly gene expression
```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
table <- filter(dat_gene, Gene == "Gly")
# Add stats
  stats <- grobTree(textGrob("N = 27\nPadjust < 0.0001", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = "Gly expression",
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative expression", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)

```

#### CuP8 gene expression
```{r}
CuP8 <- filter(dat_gene, Gene == "CuP8")
# Add stats
  stats <- grobTree(textGrob("N = 22\nPadjust < 0.0001", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  CuP8 <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = "CuP8 expression",
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative expression", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)
  
### plot Figure 3a for the MS
pCuP8<- ggboxplot(CuP8, x = "Treatment", y = "RQ", 
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative gene expression", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=15)) +
   geom_signif(comparisons = list(c("Control", "Silenced")),
                      size = 0.6,
                      textsize = 10,
                      annotations = "***",
                      tip_length = 0, 
                      vjust=0.5,
                     y_position = 4.5)
 
 #export - pdf, 3x4 inches
```

## Viral load in silenced and control mites
### test for differene in viral load, between treatment and control (Wilcoxon ranked test)
```{r Viral load stats, message=FALSE, warning=FALSE}
results_load <- data.frame()
for (gene in unique(dat_virus$Experiment))
  for (virus in unique(dat_virus$Gene)) {
    test <- wilcox.test(RQ ~ Treatment, alternative = "two.sided", data = filter(dat_virus, Experiment == gene & Gene == virus))
    results_load <- rbind(results_load, data.frame(gene = gene, virus = virus, pvalue = test$p.value))
  }
 
#We are testing the same knockdown gene several times, creating a multiple comparison problem, we fix that with a FDR correction per gene
viralLoad <- group_by(results_load, gene) %>% mutate(padj = p.adjust(pvalue, method = "fdr"))
```

#### VDV2 viral loads for silenced and control-mites
```{r}
# plot VDV2 viral loads for silenced and control-mites, in a boxplot
VDV2Load <- viralLoad %>% filter(virus == "VDV2") #%>% gsub('exp', 'VDV2')
VDV2Load$gene = gsub('exp', 'VDV2', VDV2Load$gene)
VDV2Load <- dplyr::rename(VDV2Load, Gene = gene) #i changed the colname of "gene" to "Gene". for some reason this was disturbing in "filter" function later on. 
    
datVDV2 <- filter(dat_virus, Gene == "VDV2")
datVDV2$Experiment = gsub('exp', 'VDV2', datVDV2$Experiment)

boxplotVDV2 <- list()
for (gene in unique(datVDV2$Experiment)) 
{
  table <- filter(datVDV2, Experiment == gene)
  N <- nrow(table)
  VDV2padj <- filter(VDV2Load, Gene == gene)
  Padjust <- formattable(as.double(VDV2padj[1,4], digits = 2, format = "f"))
    
# Plot
   p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = paste(gene,",Padjust=",Padjust,", n=",N),
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=8)) 
  boxplotVDV2[[gene]] <- p
}

#Padjust <- formattable(as.double(filter(VDV2Load$padj[, gene==gene[1]), digits = 2, format = "f"))
# plot the viral load of VDV2 in 9 silenced genes:
grid.arrange(boxplotVDV2$Anl, boxplotVDV2$clmd, boxplotVDV2$CuP14, boxplotVDV2$CuP8, boxplotVDV2$Glut, boxplotVDV2$Gly, boxplotVDV2$Sar, boxplotVDV2$Trans, boxplotVDV2$Twitch, nrow = 3, ncol = 3)
```

#### ARV2 viral loads for silenced and control-mites
```{r}
# plot ARV2 viral loads for silenced and control-mites, in a boxplot
ARV2Load <- filter(viralLoad, virus == "ARV2")
ARV2Load$gene = gsub('exp', 'ARV2', ARV2Load$gene)
ARV2Load <- dplyr::rename(ARV2Load, Gene = gene) #i changed the colname of "gene" to "Gene". for some reason this was disturbing in "filter" function later on. 

datARV2 <- filter(dat_virus, Gene == "ARV2")
datARV2$Experiment = gsub('exp', 'ARV2', datARV2$Experiment)

boxplotARV2 <- list()
for (gene in unique(datARV2$Experiment)) 
{
  table <- filter(datARV2, Experiment == gene)
  N <- nrow(table)
  ARV2padj <- filter(ARV2Load, Gene == gene)
  Padjust <- formattable(as.double(ARV2padj[1,4], digits = 2, format = "f"))
# Plot
   p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = paste(gene,",Padjust=",Padjust,", n=",N),
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=8)) 
  boxplotARV2[[gene]] <- p
}

# plot the viral load of ARV2 in 9 silenced genes:
grid.arrange(boxplotARV2$Anl, boxplotARV2$clmd, boxplotARV2$CuP14, boxplotARV2$CuP8, boxplotARV2$Glut, boxplotARV2$Gly, boxplotARV2$Sar, boxplotARV2$Trans, boxplotARV2$Twitch, nrow = 3, ncol = 3)
```

#### DWVa viral loads for silenced and control-mites
```{r}
# plot DWVa viral loads for silenced and control-mites, in a boxplot
DWVaLoad <- filter(viralLoad, virus == "DWVa")
DWVaLoad$gene = gsub('exp', 'DWVa', DWVaLoad$gene)
DWVaLoad <- dplyr::rename(DWVaLoad, Gene = gene) #i changed the colname of "gene" to "Gene". for some reason this was disturbing in "filter" function later on. 

datDWVa <- filter(dat_virus, Gene == "DWVa")
datDWVa$Experiment = gsub('exp', 'DWVa', datDWVa$Experiment)

boxplotDWVa <- list()
for (gene in unique(datDWVa$Experiment)) 
{
  table <- filter(datDWVa, Experiment == gene)
  N <- nrow(table)
  DWVapadj <- filter(DWVaLoad, Gene == gene)
  Padjust <- formattable(as.double(DWVapadj[1,4], digits = 2, format = "f"))
# Plot
   p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = paste(gene,",Padjust=",Padjust,", n=",N),
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=8)) 
  boxplotDWVa[[gene]] <- p
}

# plot the viral load of DWVa in 9 silenced genes:
grid.arrange(boxplotDWVa$Anl, boxplotDWVa$clmd, boxplotDWVa$CuP14, boxplotDWVa$CuP8, boxplotDWVa$Glut, boxplotDWVa$Gly, boxplotDWVa$Sar, boxplotDWVa$Trans, boxplotDWVa$Twitch, nrow = 3, ncol = 3)
```

### test for homogeneity of variances in viral load, between treatment and control
#### Levene's / Brown Forsythe test for homogeneity of variances
```{r message=FALSE, warning=FALSE}
# the default of "center" is "median" - gives the "brown forsythe" test, which is more robust, and ignores outliers,  used for > 2 group, and non-normal skewed dat_virusa.
# using center = "mean", gives the original Levene's test, which is for more symmetrical dat_virusa. 
results_variance_Levene <- data.frame()
for (gene in unique(dat_virus$Experiment))
  for (virus in unique(dat_virus$Gene)) {
    test <- leveneTest(RQ ~ Treatment, center = mean, data = filter(dat_virus, Experiment == gene & Gene == virus) )
    results_variance_Levene <- rbind(results_variance_Levene, data.frame(gene = gene, virus = virus, pvalue = test$"Pr(>F)"))
  }

#We are testing the same knockdown gene several times, creating a multiple comparison problem, we fix that with a FDR correction per gene
viralVariance_Levene <- group_by(results_variance_Levene, gene) %>% mutate(padj = p.adjust(pvalue, method = "fdr"))
```

#### each of the virus separately:
```{r  message=FALSE, warning=FALSE}
# for VDV2 in CuP8 silenced mites:
table <- filter(dat_virus, Gene == "VDV2" & Experiment == "CuP8_exp")
# Add stats
  stats <- grobTree(textGrob("N = 20\nPadjust = 0.02", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  pVDV2 <- ggdotplot(table, x = "Treatment", y = "RQ", 
          main = "VDV2 load in CuP8-silenced mites",
          color = "Treatment", fill = "Treatment",
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)

# for ARV2 in CuP8 silenced mites:
table <- filter(dat_virus, Gene == "ARV2" & Experiment == "CuP8_exp")
# Add stats
  stats <- grobTree(textGrob("N = 20\nPadjust = 0.02", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  pARV2 <- ggdotplot(table, x = "Treatment", y = "RQ", 
          main = "ARV2 load in CuP8-silenced mites",
          color = "Treatment", fill = "Treatment",
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)
  
# for DWVa in CuP8 silenced mites:
table <- filter(dat_virus, Gene == "DWVa" & Experiment == "CuP8_exp")
# Add stats
  stats <- grobTree(textGrob("N = 20\nPadjust = 0.2", x=0.5,  y=0.8, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  pDWVa <- ggdotplot(table, x = "Treatment", y = "RQ", 
          main = "DWVa load in CuP8-silenced mites",
          color = "Treatment", fill = "Treatment",
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)
  
grid.arrange(CuP8, pVDV2, pARV2,pDWVa, nrow = 1)
```


## viral load in CuP8 silenced mites - boxplots figures for MS 
```{r  message=FALSE, warning=FALSE}
### plot Figure 3a for the MS
CuP8 <- filter(dat_gene, Gene == "CuP8")
pCuP8 <- ggboxplot(CuP8, x = "Treatment", y = "RQ", 
          fill = "Treatment", palette = c("#00AFBB", "#E7B800"), lwd=2,
          order = c("Control", "Silenced"),
          ylab = "Relative gene expression", xlab = "CuP8 gene expression")  + 
          theme(axis.title.y = element_text(margin = margin(r = 10))) +
          theme(legend.position = "none", text = element_text(size=30), axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
  theme(axis.title.x = element_blank()) +
          annotate("text", -Inf, Inf, label = "CuP8", hjust = -1.9, vjust = 2,size = 9,fontface = 'italic') + 
  annotate("text", -Inf, Inf, label = "P < 0.0001", hjust = -1, vjust = 4,size = 9) 
 
### plot Figure 3b for the MS
# for VDV2 in CuP8 silenced mites:
VDV2_CuP8 <- filter(dat_virus, Gene == "VDV2" & Experiment == "CuP8_exp")

pVDV2_CuP8 <- ggboxplot(VDV2_CuP8, x = "Treatment", y = "RQ", 
                        color = "Treatment", lwd=2,
                        palette = c("#00AFBB", "#E7B800"),
                        order = c("Control", "Silenced"),
                        ylab = "Relative viral load", xlab = "VDV2 viral load") +
  theme(legend.position = "none", text = element_text(size=30), axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  theme(axis.title.x = element_blank()) +
          annotate("text", -Inf, Inf, label = "VDV2", hjust = -2.1, vjust = 2,size = 9) + 
          annotate("text", -Inf, Inf, label = "P = 0.02", hjust = -1.5, vjust = 4,size = 9) 

# for ARV2 in CuP8 silenced mites:
ARV2_CuP8 <- filter(dat_virus, Gene == "ARV2" & Experiment == "CuP8_exp")

pARV2_CuP8 <- ggboxplot(ARV2_CuP8, x = "Treatment", y = "RQ", 
                        color = "Treatment", lwd=2, 
                        palette = c("#00AFBB", "#E7B800"),
                        order = c("Control", "Silenced"),
                        ylab = "Relative viral load", xlab = "ARV-2 viral load")  + 
  theme(axis.title.y = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(legend.position = "none", text = element_text(size=30), axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
          annotate("text", -Inf, Inf, label = "ARV-2", hjust = -1.8, vjust = 2,size = 9) + 
          annotate("text", -Inf, Inf, label = "P = 0.02", hjust = -1.5, vjust = 4,size = 9)

# for DWVa in CuP8 silenced mites:
DWVa_CuP8 <- filter(dat_virus, Gene == "DWVa" & Experiment == "CuP8_exp")

pDWVa_CuP8 <- ggboxplot(DWVa_CuP8, x = "Treatment", y = "RQ", 
                        color = "Treatment", lwd=2, 
                        palette = c("#00AFBB", "#E7B800"),
                        order = c("Control", "Silenced"),
                        ylab = "Relative viral load", xlab = "DWVa viral load")  + 
              theme(axis.title.y = element_blank()) +
  theme(axis.title.x = element_blank()) +
              theme(legend.position = "none",text =   element_text(size=30),axis.text.x=element_blank(),axis.ticks.x=element_blank())  +
          annotate("text", -Inf, Inf, label = "DWVa", hjust = -1.5, vjust = 2,size = 9) + 
          annotate("text", -Inf, Inf, label = "P = 0.2", hjust = -1.3, vjust = 4,size = 9)
  
#plot CuP8 gene expression and the viruses load
grid.arrange(pCuP8, pVDV2_CuP8, pARV2_CuP8, pDWVa_CuP8 , nrow = 1)
```

## viral load in CuP8 silenced mites - boxplots figures for kakenhi proposal 
```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
CuP8 <- filter(dat_gene, Gene == "CuP8")
  
### plot the gene expression 
pCuP8 <- ggboxplot(CuP8, x = "Treatment", y = "RQ", 
          fill = "Treatment", palette = c("white", "black"), lwd=2,
          order = c("Control", "Silenced"),
          ylab = "Relative gene expression", xlab = "CuP8 gene expression")  + 
          theme(axis.title.y = element_text(margin = margin(r = 10))) +
          theme(legend.position = "none", text = element_text(size=20), axis.title.x = element_blank())

      #    +geom_signif(comparisons = list(c("Control", "Silenced")),
       #               textsize = 20,
        #              annotations = "***",
         #             y_position = 4,
          #            lwd = 0) 


# for VDV2 in CuP8 silenced mites:
VDV2_CuP8 <- filter(dat_virus, Gene == "VDV2" & Experiment == "CuP8_exp")

# Plot
pVDV2_CuP8 <- ggboxplot(VDV2_CuP8, x = "Treatment", y = "RQ", 
          fill = "Treatment", palette = c("white", "black"), lwd=2,
          order = c("Control", "Silenced"),
          ylab = "Relative viral load") +
          theme(legend.position = "none", text = element_text(size=20), axis.title.x = element_blank())

        #  +geom_signif(comparisons = list(c("Control", "Silenced")),
       #               textsize = 20,
        #              annotations = "*",
         #             y_position = 2.2,
          #            lwd = 0)

# for DWVa in CuP8 silenced mites:
DWVa_CuP8 <- filter(dat_virus, Gene == "DWVa" & Experiment == "CuP8_exp")

pDWVa_CuP8 <- ggboxplot(DWVa_CuP8, x = "Treatment", y = "RQ", 
          fill = "Treatment", palette = c("white", "black"), lwd=2,
          order = c("Control", "Silenced"),
          ylab = "Relative viral load") +
          theme(legend.position = "none", text = element_text(size=20), axis.title.y = element_blank(), axis.title.x = element_blank()) 
  
#plot CuP8 gene expression and the viruses load
grid.arrange(pVDV2_CuP8, pDWVa_CuP8 , nrow = 1)
pCuP8
```
