---
title: "Varroa virus knockdown"
output:
  html_document:
    theme: paper
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: yes
      df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load libraries
```{r libraries ,  message=FALSE, warning=FALSE, echo=FALSE}
suppressPackageStartupMessages(library(tidyverse))
library(dplyr)
library(tidyverse)
library(ggplot2)
library(Rmisc)
library(ggpubr)
library(anchors)
library(broom)
library(HDInterval)
library(coda)
library(brms)
library(devtools)
library(rjags)
library(BEST)
library(ggpubr)
library(ggthemes)
library(car) 
library(stats) 
library(moments)
library(intervcomp)
library(grid)
library(formattable)
library(gridExtra)
library(ggsignif)
library(patchwork)
library(cowplot)

```

### Load data
```{r message=FALSE, warning=FALSE, echo=FALSE}
dat_virus <- read_csv("/Users/nuriteliash/Documents/GitHub/varroa-virus-knockdown/data/virus_in_silenced.csv")
dat_gene <- read_csv("/Users/nuriteliash/Documents/GitHub/varroa-virus-knockdown/data/Silencing_qPCR.csv")
dat_gene <- dat_gene %>%
  filter((Treatment %in% c("Silenced", "Control"))) %>%
  filter(Time == "48h")
```

## Gene expression in dsRNA-treated and control mites
### test for differene in gene expression, between treatment and control (Wilcoxon ranked test)
```{r Gene expression stats, message=FALSE, warning=FALSE}
results_gene <- data.frame()
for (gene in unique(dat_gene$Gene)) 
  {
  test <- wilcox.test(RQ ~ Treatment, alternative = "two.sided", data = filter(dat_gene, Gene == gene))
    results_gene <- rbind(results_gene, data.frame(gene = gene, pvalue = test$p.value))
  }

#We are testing the same knockdown gene several times, creating a multiple comparison problem, we fix that with a FDR correction per gene
### for some reason - the adjusted p-values are the same as the original p-vlaues!
geneExp <- group_by(results_gene, gene) %>% 
  mutate(padj = p.adjust(pvalue, method = "fdr"))
geneExp <- dplyr::rename(geneExp, Gene = gene) #i changed the colname of "gene" to "Gene". for some reason this was disturbing in "filter" function later on. 

# plot all genes expression for silenced and control-mites, in a boxplot
boxplot <- list()
for (gene in unique(dat_gene$Gene)) 
{
  table <- filter(dat_gene, Gene == gene)
  N <- nrow(table)
geneExppadj <- filter(geneExp, Gene == gene)
  Padjust <- formattable(as.double(geneExppadj[1,3], digits = 2, format = "f"))
  # Plot
   p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = paste(gene,",Padjust=",Padjust,", n=",N),
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative expression", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=8)) 
  boxplot[[gene]] <- p
}

# plot all 11 genes in one figure
grid.arrange(boxplot$Anl, boxplot$clmd, boxplot$Chl, boxplot$CuP14, boxplot$CuP8, boxplot$Glut, boxplot$Gly, boxplot$HDD, boxplot$Prolin, boxplot$Sar, boxplot$Trans, boxplot$Twitch, nrow = 3, ncol = 4)
#lapply(boxplot, grid.arrange, nrow = 4, ncol = 3)
```

#### Gly gene expression
```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
table <- filter(dat_gene, Gene == "Gly")
# Add stats
  stats <- grobTree(textGrob("N = 27\nPadjust < 0.0001", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = "Gly expression",
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative expression", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)

```

## CuP8 gene expression for the MS Figrue 3a:
```{r}
CuP8 <- filter(dat_gene, Gene == "CuP8")
# Add stats
  stats <- grobTree(textGrob("N = 22\nPadjust < 0.0001", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  CuP8 <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = "CuP8 expression",
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative expression", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)
  
### plot Figure 3a for the MS
pCuP8<- ggboxplot(CuP8, x = "Treatment", y = "RQ", 
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative gene expression", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=15)) +
   geom_signif(comparisons = list(c("Control", "Silenced")),
                      size = 0.6,
                      textsize = 10,
                      annotations = "***",
                      tip_length = 0, 
                      vjust=0.5,
                     y_position = 4.5)
 
 #export - pdf, 3x4 inches
```

## Viral load in silenced and control mites
### test for differene in viral load, between treatment and control (Wilcoxon ranked test)
```{r Viral load stats, message=FALSE, warning=FALSE}
results_load <- data.frame()
for (gene in unique(dat_virus$Experiment))
  for (virus in unique(dat_virus$Gene)) {
    test <- wilcox.test(RQ ~ Treatment, alternative = "two.sided", data = filter(dat_virus, Experiment == gene & Gene == virus))
    results_load <- rbind(results_load, data.frame(gene = gene, virus = virus, pvalue = test$p.value))
  }
 
#We are testing the same knockdown gene several times, creating a multiple comparison problem, we fix that with a FDR correction per gene
viralLoad <- group_by(results_load, gene) %>% mutate(padj = p.adjust(pvalue, method = "fdr"))
```

VDV2 viral loads for silenced and control-mites
```{r}
# plot VDV2 viral loads for silenced and control-mites, in a boxplot
VDV2Load <- viralLoad %>% filter(virus == "VDV2") #%>% gsub('exp', 'VDV2')
VDV2Load$gene = gsub('exp', 'VDV2', VDV2Load$gene)
VDV2Load <- dplyr::rename(VDV2Load, Gene = gene) #i changed the colname of "gene" to "Gene". for some reason this was disturbing in "filter" function later on. 
    
datVDV2 <- filter(dat_virus, Gene == "VDV2")
datVDV2$Experiment = gsub('exp', 'VDV2', datVDV2$Experiment)

boxplotVDV2 <- list()
for (gene in unique(datVDV2$Experiment)) 
{
  table <- filter(datVDV2, Experiment == gene)
  N <- nrow(table)
  VDV2padj <- filter(VDV2Load, Gene == gene)
  Padjust <- formattable(as.double(VDV2padj[1,4], digits = 2, format = "f"))
    
# Plot
   p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = paste(gene,",Padjust=",Padjust,", n=",N),
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=8)) 
  boxplotVDV2[[gene]] <- p
}

#Padjust <- formattable(as.double(filter(VDV2Load$padj[, gene==gene[1]), digits = 2, format = "f"))
# plot the viral load of VDV2 in 9 silenced genes:
grid.arrange(boxplotVDV2$Anl, boxplotVDV2$clmd, boxplotVDV2$CuP14, boxplotVDV2$CuP8, boxplotVDV2$Glut, boxplotVDV2$Gly, boxplotVDV2$Sar, boxplotVDV2$Trans, boxplotVDV2$Twitch, nrow = 3, ncol = 3)
```

ARV2 viral loads for silenced and control-mites
```{r}
# plot ARV2 viral loads for silenced and control-mites, in a boxplot
ARV2Load <- filter(viralLoad, virus == "ARV2")
ARV2Load$gene = gsub('exp', 'ARV2', ARV2Load$gene)
ARV2Load <- dplyr::rename(ARV2Load, Gene = gene) #i changed the colname of "gene" to "Gene". for some reason this was disturbing in "filter" function later on. 

datARV2 <- filter(dat_virus, Gene == "ARV2")
datARV2$Experiment = gsub('exp', 'ARV2', datARV2$Experiment)

boxplotARV2 <- list()
for (gene in unique(datARV2$Experiment)) 
{
  table <- filter(datARV2, Experiment == gene)
  N <- nrow(table)
  ARV2padj <- filter(ARV2Load, Gene == gene)
  Padjust <- formattable(as.double(ARV2padj[1,4], digits = 2, format = "f"))
# Plot
   p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = paste(gene,",Padjust=",Padjust,", n=",N),
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=8)) 
  boxplotARV2[[gene]] <- p
}

# plot the viral load of ARV2 in 9 silenced genes:
grid.arrange(boxplotARV2$Anl, boxplotARV2$clmd, boxplotARV2$CuP14, boxplotARV2$CuP8, boxplotARV2$Glut, boxplotARV2$Gly, boxplotARV2$Sar, boxplotARV2$Trans, boxplotARV2$Twitch, nrow = 3, ncol = 3)
```

DWVa viral loads for silenced and control-mites
```{r}
# plot DWVa viral loads for silenced and control-mites, in a boxplot
DWVaLoad <- filter(viralLoad, virus == "DWVa")
DWVaLoad$gene = gsub('exp', 'DWVa', DWVaLoad$gene)
DWVaLoad <- dplyr::rename(DWVaLoad, Gene = gene) #i changed the colname of "gene" to "Gene". for some reason this was disturbing in "filter" function later on. 

datDWVa <- filter(dat_virus, Gene == "DWVa")
datDWVa$Experiment = gsub('exp', 'DWVa', datDWVa$Experiment)

boxplotDWVa <- list()
for (gene in unique(datDWVa$Experiment)) 
{
  table <- filter(datDWVa, Experiment == gene)
  N <- nrow(table)
  DWVapadj <- filter(DWVaLoad, Gene == gene)
  Padjust <- formattable(as.double(DWVapadj[1,4], digits = 2, format = "f"))
# Plot
   p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = paste(gene,",Padjust=",Padjust,", n=",N),
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=8)) 
  boxplotDWVa[[gene]] <- p
}

# plot the viral load of DWVa in 9 silenced genes:
grid.arrange(boxplotDWVa$Anl, boxplotDWVa$clmd, boxplotDWVa$CuP14, boxplotDWVa$CuP8, boxplotDWVa$Glut, boxplotDWVa$Gly, boxplotDWVa$Sar, boxplotDWVa$Trans, boxplotDWVa$Twitch, nrow = 3, ncol = 3)
```

### test for homogeneity of variances in viral load, between treatment and control
#### Levene's / Brown Forsythe test for homogeneity of variances
```{r message=FALSE, warning=FALSE}
# the default of "center" is "median" - gives the "brown forsythe" test, which is more robust, and ignores outliers,  used for > 2 group, and non-normal skewed dat_virusa.
# using center = "mean", gives the original Levene's test, which is for more symmetrical dat_virusa. 
results_variance_Levene <- data.frame()
for (gene in unique(dat_virus$Experiment))
  for (virus in unique(dat_virus$Gene)) {
    test <- leveneTest(RQ ~ Treatment, center = mean, data = filter(dat_virus, Experiment == gene & Gene == virus) )
    results_variance_Levene <- rbind(results_variance_Levene, data.frame(gene = gene, virus = virus, pvalue = test$"Pr(>F)"))
  }

#We are testing the same knockdown gene several times, creating a multiple comparison problem, we fix that with a FDR correction per gene
viralVariance_Levene <- group_by(results_variance_Levene, gene) %>% mutate(padj = p.adjust(pvalue, method = "fdr"))
```

each of the virus separately:
```{r  message=FALSE, warning=FALSE}
# for VDV2 in CuP8 silenced mites:
table <- filter(dat_virus, Gene == "VDV2" & Experiment == "CuP8_exp")
# Add stats
  stats <- grobTree(textGrob("N = 20\nPadjust = 0.02", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  pVDV2 <- ggdotplot(table, x = "Treatment", y = "RQ", 
          main = "VDV2 load in CuP8-silenced mites",
          color = "Treatment", fill = "Treatment",
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)

# for ARV2 in CuP8 silenced mites:
table <- filter(dat_virus, Gene == "ARV2" & Experiment == "CuP8_exp")
# Add stats
  stats <- grobTree(textGrob("N = 20\nPadjust = 0.02", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  pARV2 <- ggdotplot(table, x = "Treatment", y = "RQ", 
          main = "ARV2 load in CuP8-silenced mites",
          color = "Treatment", fill = "Treatment",
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)
  
# for DWVa in CuP8 silenced mites:
table <- filter(dat_virus, Gene == "DWVa" & Experiment == "CuP8_exp")
# Add stats
  stats <- grobTree(textGrob("N = 20\nPadjust = 0.2", x=0.5,  y=0.8, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  pDWVa <- ggdotplot(table, x = "Treatment", y = "RQ", 
          main = "DWVa load in CuP8-silenced mites",
          color = "Treatment", fill = "Treatment",
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)
  
grid.arrange(CuP8, pVDV2, pARV2,pDWVa, nrow = 1)
```


#### for CuP8 silenced mites - boxplots
viruses in CuP8 silenced mites, for MS
```{r  message=FALSE, warning=FALSE}
CuP8 <- filter(dat_gene, Gene == "CuP8")
  
### plot Figure 3a for the MS
pCuP8<- ggboxplot(CuP8, x = "Treatment", y = "RQ", 
          fill = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative gene expression", xlab = "CuP8 gene expression")  + 
          theme(legend.position = "none", text = element_text(size=15), axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1)) +
          geom_signif(comparisons = list(c("Control", "Silenced")),
                      size = 0.6,
                      textsize = 10,
                      annotations = "***",
                      tip_length = 0, 
                      vjust=0.5,
                     margin_top = 0.06) 

#transparet fill:
# fill = "Treatment", palette = c("#00AFBB99", "#E7B80099"),
# no titles:
# theme(axis.title.x = element_blank()) 

# for VDV2 in CuP8 silenced mites:
VDV2_CuP8 <- filter(dat_virus, Gene == "VDV2" & Experiment == "CuP8_exp")

# Plot
pVDV2_CuP8 <- ggboxplot(VDV2_CuP8, x = "Treatment", y = "RQ", 
          color = "Treatment", 
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "VDV2 viral load") +
          theme(legend.position = "none", text = element_text(size=15), axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
          geom_signif(comparisons = list(c("Control", "Silenced")),
                      size = 0.6,
                      textsize = 10,
                      annotations = "*",
                      tip_length = 0, 
                      vjust=0.5,
                      margin_top = 0.06)

# for ARV2 in CuP8 silenced mites:
ARV2_CuP8 <- filter(dat_virus, Gene == "ARV2" & Experiment == "CuP8_exp")

# Plot
pARV2_CuP8 <- ggboxplot(ARV2_CuP8, x = "Treatment", y = "RQ", 
          color = "Treatment", 
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "ARV-2 viral load")  + 
          theme(axis.title.y = element_blank()) +
          theme(legend.position = "none", text = element_text(size=15), axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
          geom_signif(comparisons = list(c("Control", "Silenced")),
                      size = 0.6,
                      textsize = 10,
                      annotations = "*",
                      tip_length = 0, 
                      vjust=0.5,
                     margin_top = 0.06)
  
# for DWVa in CuP8 silenced mites:
DWVa_CuP8 <- filter(dat_virus, Gene == "DWVa" & Experiment == "CuP8_exp")

# Plot
pDWVa_CuP8 <- ggboxplot(DWVa_CuP8, x = "Treatment", y = "RQ", 
          color = "Treatment", 
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "DWVa viral load")  + 
          theme(axis.title.y = element_blank()) +
          theme(legend.position = c(0.8, 0.8),text = element_text(size=15), axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
          geom_signif(comparisons = list(c("Control", "Silenced")),
                      size = 0.6,
                      textsize = 5,
                      annotations = "NS",
                      tip_length = 0, 
                      margin_top = 0.06)
  
#plot CuP8 gene expression and the viruses load
grid.arrange(pCuP8,  pVDV2_CuP8, pARV2_CuP8, pDWVa_CuP8 , nrow = 1)

# another option
# arrange the three plots in a single row
prow <- plot_grid( pCuP8 + theme(legend.position="none"),
           pVDV2_CuP8 + theme(legend.position="none"),
           pARV2_CuP8 + theme(legend.position="none"),
           pDWVa_CuP8 + theme(legend.position="none"),
             align = 'vh',
           hjust = -1,
           nrow = 1
           )
legend_gene <- get_legend(pCuP8 + theme(legend.position="bottom"))
plot_grid( prow, legend_gene, ncol = 1, rel_heights = c(1, .2))


# another option
#arragen viruses plots
pvirus <- plot_grid(pVDV2_CuP8 + theme(legend.position="none"),
           pARV2_CuP8 + theme(legend.position="none"),
           pDWVa_CuP8 + theme(legend.position="none"),
             align = 'vh',
           hjust = -1,
           nrow = 1) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

# arrange the three plots in a single row
prow <- plot_grid( pCuP8 + theme(legend.position="none"),
           pvirus,
             align = 'vh',
           hjust = -1,
           nrow = 1
           )
legend_gene <- get_legend(pCuP8 + theme(legend.position="bottom"))
plot_grid( prow, legend_gene, ncol = 1, rel_heights = c(1, .2))
# legend.position = "horizontal", 
```






#### for Gly silenced mites
```{r  message=FALSE, warning=FALSE}
# for VDV2 in Gly silenced mites:
table <- filter(dat_virus, Gene == "VDV2" & Experiment == "Gly_exp")
# Add stats
  stats <- grobTree(textGrob("N = 22\nPadjust = 0.84", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  p <- ggdotplot(table, x = "Treatment", y = "RQ", 
          main = "VDV2 load in Gly-silenced mites",
          color = "Treatment", fill = "Treatment",
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)

# for ARV2 in Gly silenced mites:
table <- filter(dat_virus, Gene == "ARV2" & Experiment == "Gly_exp")
# Add stats
  stats <- grobTree(textGrob("N = 22\nPadjust = 0.84", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  p <- ggdotplot(table, x = "Treatment", y = "RQ", 
          main = "ARV2 load in Gly-silenced mites",
          color = "Treatment", fill = "Treatment",
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)
  
# for DWVa in Gly silenced mites:
table <- filter(dat_virus, Gene == "DWVa" & Experiment == "Gly_exp")
# Add stats
  stats <- grobTree(textGrob("N = 22\nPadjust = 0.84", x=0.5,  y=0.9, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  p <- ggdotplot(table, x = "Treatment", y = "RQ", 
          main = "DWVa load in Gly-silenced mites",
          color = "Treatment", fill = "Treatment",
          palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative viral load", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)
```
#### Fligner-Killeen test for homogeneity of variances
```{r eval=FALSE, include=FALSE, message=FALSE, warning=FALSE}
results_variance_FK <- dat_virusa.frame()
for (gene in unique(dat_virus$Experiment))
  for (virus in unique(dat_virus$Gene)) {
    test <- fligner.test(RQ ~ Treatment, data = filter(dat_virus, Experiment == gene & Gene == virus) )
    results_variance_FK <- rbind(results_variance_FK, data.frame(gene = gene, virus = virus, pvalue = test$p.value))
  }

#We are testing the same knockdown gene several times, creating a multiple comparison problem, we fix that with a FDR correction per gene
viralVariance_FK <- group_by(results_variance_FK, gene) %>% mutate(padj = p.adjust(pvalue, method = "fdr"))
```
####  Bonett-Seier t-test for comparing variability measures of two independent samples.
```{r eval=FALSE, include=FALSE,  message=FALSE, warning=FALSE}
# the default of "center" is "median" - gives the "brown forsythe" test, which is more robust, and ignores outliers,  used for > 2 group, and non-normal skewed dat_virusa.
# using center = "mean", gives the original Levene's test, which is for more symmetrical dat_virusa. 
results_variance_Bonett <- dat_virusa.frame()
for (gene in unique(dat_virus$Experiment))
  for (virus in unique(dat_virus$Gene)) {
    test <- Bonett.Seier.test(x = Treatment, y = RQ, alternative = c("two.sided", "less", "greater"),
  alpha = 0.05, data = filter(dat_virus, Experiment == gene & Gene == virus) )
    results_variance_Bonett <- rbind(results_variance_Bonett, data.frame(gene = gene, virus = virus, pvalue = test$"Pr(>F)"))
  }

#We are testing the same knockdown gene several times, creating a multiple comparison problem, we fix that with a FDR correction per gene
viralVariance_Bonett <- group_by(results_variance_Bonett, gene) %>% mutate(padj = p.adjust(pvalue, method = "fdr"))


x = dat_virus %>%
  filter(Experiment == "clmd_exp") %>%
  filter(Gene == "DWVa") %>%
  filter(Treatment == "Silenced")

y = dat_virus %>%
  filter(Experiment == "clmd_exp") %>%
  filter(Gene == "DWVa") %>%
  filter(Treatment == "Control")
  
test <- Bonett.Seier.test(x = x$RQ , y$RQ , alternative = c("two.sided", "less", "greater"), alpha = 0.05)
  
viralVariance_Bonett <- group_by(results_variance_Bonett, gene) %>% mutate(padj = p.adjust(pvalue, method = "fdr"))

```




#old loop:
geneLevel <- unique(dat_gene$Gene)
sizeGrWindow(9,6)
par(mfrow=c(2,as.integer(0.5+length(geneLevel)/2)))
par(mar = c(4,5,3,1))
boxplot <- list()
for (gene in c(1:length(geneLevel))) 
  {
  table <- filter(dat_gene, Gene == gene)
  N <- nrow(table)
  Padjust <- geneExp %>% filter(gene == gene)
# Add stats
  stats <- grobTree(textGrob("N = ", paste(N),"\n", "Padjust = ",paste(as.double(Padjust$padj[1])),"", x=0.6,  y=0.8, hjust=0,
  gp=gpar(col="black", fontsize=20)))
# Plot
  p <- ggboxplot(table, x = "Treatment", y = "RQ", 
          main = gene,
          color = "Treatment", palette = c("#00AFBB", "#E7B800"),
          order = c("Control", "Silenced"),
          ylab = "Relative expression", xlab = "Treatment")  + 
          theme(legend.position = "none", text = element_text(size=20)) + 
          annotation_custom(stats)
  boxplot[[gene]] <- p
}